---
title: "Report"
author: "Khalida Dushimova, Richard Efraim Langi, Madleen Piegsa, Greta Karathanos"
date: '2022-07-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Introduction

RNA-binding proteins are proteins that bind to the double or single stranded RNA in cells and by this interact with transcripts of RNA-driven processes. This large group of proteins play key roles in RNA processing and modification (Alternative splicing, RNA editing and polyadenylation), export, mRNA localization and translation. The malfunction of RBP´s underlies the origin of many diseases from neurogenerative disorders to cancer.  Therefore, it is necessary to increase the number of recognized RBP´s and the understanding of their molecular mechanisms.
For that reason, M.Caudron-Herger et al. created R-Deep with the aim to detect RBP´s automatically. In general, R-Deep is a proteome-wide, unbiased, and enrichment-free screen based on density gradient ultracentrifugation.

2. Materials and Methods

RDeep
R-DeeP is a proteome-wide, unbiased and enrichment-free screen. The principle of R-DeeP is based on cellular lysate fractionation by density gradient ultracentrifugation.The outcome is analyzed by proteome-wide mass spectometry or individual western blotting. In general, R-DeeP is used to determine RNA-dependent protein, that interact directly or indirectly with RNA. Lysates with (RNase group) and without (Ctrl group) RNase treatment are compared. By that differences in molecular weight, hence and the size of the complexes are determined.RBPs are expected to split after RNase treatment and migrate to different fractions in a sucrose density gradient.

```{r}
#(Bild RDEEP selbstgezeichnet einfügen)
```



Dataset exploration
Our given dataset consists of mass-spectometry data from non-synchronized A549 cells which are human lung carcinoma cells of a caucasian male. In general, the data show the protein amount of each of our 3680 human proteins per fraction. The RDeep screen has been repeated three times so it comprises three replicates for each sample. All in all, we got 3680 rows with one human proteins per row and 150 columns for our Ctrl and RNase group for 25 fractions and three replicates each. 

Fractionwise Normalization
The total amount of protein of every replicate should be similar. In our given dataset this was not the case. Normalization is the process to account for the bias and make samples more comparable. Our aim was to change the values of columns to a common scale without distorting differences in the range of values and by this reducing the variation between our three technical replicates.
Therefore, for our first normalization we compute the sums fractionwise and find the two closest sums. We then define normalization factors for the replicates. The quotients of the mean sums and sums of replicates are the normalization factors. 

Anti-outlier function
For our second normalization, we defined the mean out of the two most similar replicates and by this wrote an own function to exclude outliers. The outliers were found, removed, and replaced by the mean of the other two most similar replicates. 


Peaks identification

Peaks We expect RNA dependent proteins to migrate to migrate to different positions in the RNase treated sample compared to the Ctrl sample. As a next step we identify the maxima in both samples to characterize a protein as RNA dependent or RNA independent. We detect the local and the global maxima to draw all the biological information we could possibly get from our given values.
Our theoretical maximum is a point x whose neighboring values have to be smaller. 

The method is based on checking the neighbours of each fraction. For the first fraction, only the right neighbour will be compared because there is no left neighbour. For the second till twenty fourth fraction, both left and right neighbours will be compared. For the last fraction, only the left neighbour will be compared since right neighbour doesn't exist. If the the checked fraction have higher values than the neighbour(s), then the fraction is a maxima. If the the checked fraction have lower values than the neighbour(s), then the fraction is a not a maxima and will be zero-ed in our code.

```{r}
#(Bild selbstgemalt Maxima detection)

```

Criteria for RNA dependency

T-Test of absolute maxima 

T-Test of global maxima
T-Test shows us if the global maxima of each of the proteins (all replicates) between Ctrl and RNase group has a significant difference. We declare a significant difference between both groups as RNA dependent. It will be our first criteria for RNA dependency.


K-Means Clustering (Y-shift and X-shift detection)
K-Means Clustering is an unsupervised non-linear algorithm that clusters data based on similarity. Its aim is to partition the observations into a previously definded number of clusters. We define this number by performing the elbow method. (Bild von Carls Vorlesung zu Kmeans?)
Through K-Means Clustering and comparing our t-test results, we define selection criteria (Y-shift and X-shift) to determine RNA dependent proteins. Y-shift is the difference of protein amount between the global maxima of Ctrl and RNase group. X-shift is the difference of locations of global maxima (fraction) between the global maxima of Ctrl and RNase group. 

T-Test of local maxima




Linear regression
Finally, we perform a linear regression. This model can generally be used to model the relationship between a dependent variable (regressand) and one or more explanatory variables (predictors). The relationship is represented by a linear function. We can see from the model to what extent the dependent variable can be explained by the other variables. 
Our regression model predicts the Y-Shift values with the information from correlation between Ctrl and RNase.









Results 

Fractionwise Normalization 

After we run the fractionwise normalization the protein amount between the three replicates of RNase dataframe and the three replicates of the Ctrl dataframe is equal. This can be seen in the barplot. The barplot also shows that although the protein amount of all three replicates of Ctrl and RNase is equal, there is a difference between the total amount of Ctrl ans RNase, which is exactly what we need. 

```{r}
##barplot einfügen
```


Anti outlier function 
The comparison of the MICA_HUMAN_Ctrl before and after the application of the anti_outlier_function has shown that the function reduced the outliers. Now the three replicates are comparable. 

```{r}
# plots einfügen
```


Peaks Identification 

For the local maxima we decided to use a threshold value of 40% of the global maxima. Our chosen threshold of 40% protein value is enough to get only significant maxima and reduce the effect of noisy data. 


```{r}
# von Greta gemaltes Bild einfügen
```



Criteria for RNA dependency



T-Test of global and local maxima

A data frame **test** with 3680 rows and 1 column is produced after performing t test of global maxima between Ctrl and RNase group. The row represents the name of the proteins that is alphabetically ordered. The only column represents the RNA dependency with 2 kind of results, TRUE or FALSE.

For t test of local maxima, the result is a data frame **test_0.4** that consists of 3680 rows and 1 column. The name of the proteins are in rows and the only column shows the RNA dependency. 3 outcomes are generated, TRUE, FALSE or NA.

```{r}
#Tabelle einfügen mit den TRUE/FALSE Ergebnissen 
```



K-Means Clustering (Y-shift and X-shift detection)

```{r}
#Bild einfügen
```






K-means clustering 

If the X- and Y-shift has positive values (left and down shift), we define the protein as RNA dependent. If the X- and Y-shift has negative values or close to zero (right and up shift), we define the protein as RNA independent. These shifts will be our second criteria for RNA dependency. We also combined our X- and Y-shifts in a dataframe and used the elbow method to determine the optimal number of clusters.	


Comparison of RNA dependency of both t-Test and K-Means
"Match" shows 1 (True) and 0 (False). True means that the results from T-Test in terms of RNA (in)dependency is the same as K-Means and the other way around for False. We have defined 2 Criteria for RNA dependency. The first is the result from T-test where a significant difference of the absolute maxima means that the protein is RNA-dependent. The second one is the result from K-Means clustering. Here proteins grouped in a cluster with a positive Y-Shift are defined as RNA-depedent. Below we consider 2 cases. First when both criteria are fulfilled and the other one when either criteria is satisfied.


Linear Regression model 

The first linear regression is performed between correlation in x axis and y shift in y axis. The linear equation from the regression is $y = 1690907x - 1184175$. The p value for the predictor variable y is 7.98e^-06^ and for x is 5.96e^-09^. The p value of our model is 5.962e^-09^. A more detailed overview of of the regression **summary(lm)** can be seen in the picture below.

```{r}
picture
```

The histogram of the residues shows that the residuals are between -2e^-07^ and 2e^-07^. The QQ plot of the theoretical and sample residues aligns with the QQ line except when the theoretical quantiles are below -2.5 and above 2.5. 

```{r}
picture
```

The last plot is a plot with actual value in x axis, predicted value in y axis and a linear line with intercept 0 and slope 1. The data points gather mostly on the place where the predicted and actual values are above 0. Below 0 there are only few points are near the linear line. Nonetheless, there are also some points that are very far from the linear line.


```{r}
picture
```

The second linear regression is performed between RBP2GOScore in x axis and x shift in y axis. The linear equation from the regression is $y = 0.069630x -0.368093$. The p value for the predictor variable y is 0.00285 and for x is 2e^-16^. The p value of our model is 2.2e^-16^. A more detailed overview of of the regression **summary(lm_4)** can be seen in the picture below.

```{r}
picture
```

The histogram of the residues shows that the residuals are between -10 and 20. The QQ plot of the theoretical and sample residues aligns with the QQ line except when the theoretical quantiles are below -1.5 and above 1. 

```{r}
picture
```

The last plot is a plot with actual value in x axis, predicted value in y axis and a linear line with intercept 0 and slope 1. The data points gather mostly near the linear line when the actual value is between -2 and 2 and the predicted value is around 0.5.


```{r}
picture
```



Discussion 



Peaks Identification
	
The RNA-dependent protein complex  will dissociate and individual proteins will migrate in different fractions.
Analysis of the protein content of fractions by comparing Ctrl and RNAse samples allows us to identify RNA-dependent shifts.
To define these shifts, we wrote an own maxima detection function that detects global as well as local peaks. Using the threshold, we only detect
maxima with a certain significance. Our chosen threshold of 40% protein value is enough to get only significant maxima. 






Conclusion 

True positive and true negative rate 


